Effects of CHILDREN's programs

### 2020-02-27 paper.tex
lg

\begin{table}
\begin{center}
\begin{tabular}{l c c }
\hline
 & Model 1 & Model 2 \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              \\
                 & $(0.57)$        &              \\
realTripsSubsidy &                 & $0.00^{*}$   \\
                 &                 & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         \\
Num. obs.        & 329             & 322          \\
RMSE             & 39992.79        & 2.96         \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Statistical models}
\label{mealsTripsSubsidyRegressions}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{fundamentalDynamics} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM

@@

 [3] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            

@@

[23] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            

@@

\usepackage{booktabs}

\begin{table}
\caption{Regression Results: Number of meals}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\toprule
 & OLS & OLS without Outliers & OLS Impute \\
\midrule
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\midrule
R$^2$       & 0.43            & 0.13            & 0.45             \\
Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
Num. obs.   & 329             & 250             & 440              \\
RMSE        & 39992.79        & 3629.72         & 39601.41         \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{GrantsRegressionsLunch}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c }
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.7049^{***}$ & $2.6236^{***}$ & $3.6237^{***}$ \\
                 & $(0.3313)$     & $(0.2300)$     & $(0.3253)$     \\
realTripsSubsidy & $0.0002^{*}$   & $0.0003^{***}$ & $0.0002^{*}$   \\
                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
\hline
R$^2$            & 0.0474         & 0.0880         & 0.0504         \\
Adj. R$^2$       & 0.0444         & 0.0844         & 0.0476         \\
Num. obs.        & 322            & 257            & 334            \\
RMSE             & 2.9565         & 1.6981         & 2.9310         \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{GrantsRegressionsTrips}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{SelfworthRegressions}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 2:47:06 PM
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% #normal weights selfworth& subsidiy
% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% 
% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
% @

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l c c}
\hline
 & Model 1 & Model 2 \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              \\
                 & $(0.57)$        &              \\
realTripsSubsidy &                 & $0.00^{*}$   \\
                 &                 & $(0.00)$     \\
\hline
R$^2$            & $0.43$          & $0.05$       \\
Adj. R$^2$       & $0.43$          & $0.04$       \\
Num. obs.        & $329$           & $322$        \\
RMSE             & $39992.79$      & $2.96$       \\
\hline
\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\caption{Statistical models}
\label{mealsTripsSubsidyRegressions}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Do, Feb 27, 2020 - 17:09:29
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{fundamentalDynamics} 
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

% Date and time: Do, Feb 27, 2020 - 17:09:29

@@

 [3] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               

@@

[23] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               

@@

\usepackage{graphicx}
\usepackage{booktabs}

\begin{table}
\caption{Regression Results: Number of meals}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c}
\toprule
 & OLS & OLS without Outliers & OLS Impute \\
\midrule
(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
\midrule
R$^2$       & $0.43$          & $0.13$          & $0.45$           \\
Adj. R$^2$  & $0.43$          & $0.12$          & $0.45$           \\
Num. obs.   & $329$           & $250$           & $440$            \\
RMSE        & $39992.79$      & $3629.72$       & $39601.41$       \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
aliquyam. \\ $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
\end{tabular}
}
\label{GrantsRegressionsLunch}
\end{center}
\end{table}

@@

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c}
\hline
 & OLS & OLS without Outliers & OLS Impute \\
\hline
(Intercept)      & $3.7049^{***}$ & $2.6236^{***}$ & $3.6237^{***}$ \\
                 & $(0.3313)$     & $(0.2300)$     & $(0.3253)$     \\
realTripsSubsidy & $0.0002^{*}$   & $0.0003^{***}$ & $0.0002^{*}$   \\
                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
\hline
R$^2$            & $0.0474$       & $0.0880$       & $0.0504$       \\
Adj. R$^2$       & $0.0444$       & $0.0844$       & $0.0476$       \\
Num. obs.        & $322$          & $257$          & $334$          \\
RMSE             & $2.9565$       & $1.6981$       & $2.9310$       \\
\hline
\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Number of trips}
\label{GrantsRegressionsTrips}
\end{center}
\end{table}

@@

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
Num. obs.                      & $428$    & $184$    & $430$    & $187$    \\
RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Selfworth}
\label{SelfworthRegressions}
\end{center}
\end{table}

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
Num. obs.                      & $426$    & $177$    & $429$    & $181$    \\
RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: dayToDaySkills}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       \\
Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       \\
Num. obs.           & $121$        & $120$       & $177$        & $177$        \\
RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less Ill}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   \\
Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   \\
Num. obs.           & $214$    & $212$    & $275$      & $275$    \\
RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Dietary Knowledge}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     \\
Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    \\
Num. obs.           & $213$        & $211$    & $274$        & $274$      \\
RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Appreciate Healthy}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Do, Feb 27, 2020 - 17:09:35
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% 
% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
% @

\usepackage{graphicx}

\begin{table}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c}
\hline
 & OLS & WLS & OLS Impute & WLS Impute \\
\hline
(Intercept)               & $-1.08^{***}$ & $-0.99^{**}$ & $-0.04$      & $-0.08$    \\
                          & $(0.24)$      & $(0.30)$     & $(0.18)$     & $(0.20)$   \\
DGECriteriaNoScaled       & $0.34^{***}$  & $0.36^{***}$ & $0.23^{***}$ & $0.27$     \\
                          & $(0.08)$      & $(0.06)$     & $(0.07)$     & $(0.14)$   \\
regionalProducts\_scaled  & $0.02$        & $-0.03$      & $0.11$       & $0.02$     \\
                          & $(0.08)$      & $(0.11)$     & $(0.07)$     & $(0.11)$   \\
yearsSupportSince         & $0.02$        & $-0.03$      & $0.01$       & $0.05^{*}$ \\
                          & $(0.03)$      & $(0.04)$     & $(0.02)$     & $(0.02)$   \\
realSubsidyPerBeneficiary & $-0.00$       & $0.00$       & $0.00$       & $-0.00$    \\
                          & $(0.00)$      & $(0.00)$     & $(0.00)$     & $(0.00)$   \\
stateBayern               & $0.96^{**}$   & $1.88^{***}$ &              &            \\
                          & $(0.33)$      & $(0.49)$     &              &            \\
stateBerlin               & $1.09^{**}$   & $1.34^{***}$ &              &            \\
                          & $(0.37)$      & $(0.37)$     &              &            \\
stateBrandenburg          & $2.21^{***}$  & $2.46^{***}$ &              &            \\
                          & $(0.43)$      & $(0.40)$     &              &            \\
stateBremen               & $1.00$        & $1.03$       &              &            \\
                          & $(0.58)$      & $(0.59)$     &              &            \\
stateHamburg              & $0.95$        & $1.96^{***}$ &              &            \\
                          & $(0.67)$      & $(0.40)$     &              &            \\
stateHessen               & $0.87^{***}$  & $1.16^{***}$ &              &            \\
                          & $(0.23)$      & $(0.31)$     &              &            \\
stateMV                   & $0.09$        & $0.14$       &              &            \\
                          & $(0.21)$      & $(0.26)$     &              &            \\
stateNiedersachsen        & $2.48^{***}$  & $2.30^{***}$ &              &            \\
                          & $(0.40)$      & $(0.43)$     &              &            \\
stateNRW                  & $0.68^{*}$    & $1.00^{**}$  &              &            \\
                          & $(0.27)$      & $(0.33)$     &              &            \\
stateSaarland             & $1.50^{***}$  & $1.75^{***}$ &              &            \\
                          & $(0.32)$      & $(0.25)$     &              &            \\
stateSachsen              & $1.34^{***}$  & $1.23^{***}$ &              &            \\
                          & $(0.27)$      & $(0.27)$     &              &            \\
stateSchleswig-Holstein   & $1.33^{***}$  & $1.63^{***}$ &              &            \\
                          & $(0.37)$      & $(0.42)$     &              &            \\
stateThüringen            & $0.99$        & $1.29^{*}$   &              &            \\
                          & $(0.59)$      & $(0.55)$     &              &            \\
\hline
R$^2$                     & $0.51$        & $0.73$       & $0.09$       & $0.22$     \\
Adj. R$^2$                & $0.39$        & $0.66$       & $0.07$       & $0.20$     \\
Num. obs.                 & $88$          & $88$         & $175$        & $175$      \\
RMSE                      & $0.73$        & $5.62$       & $0.94$       & $7.77$     \\
\hline
\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
}
\caption{Regression Results: Less ill expanded model}
\label{expandLessIll}
\end{center}
\end{table}
